\documentclass[12pt,a4paper]{report}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{geometry}

% Page geometry
\geometry{
    left=1.5in,
    right=1in,
    top=1in,
    bottom=1in
}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue,
}

% Code listing setup
\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray},
}

% Title page information
\title{
    \textbf{Explainable AI for Docker Container Malware Detection\
    Using Vision Transformers}\
    \vspace{1cm}
    \large MTech Thesis\
    Indian Institute of Information Technology Guwahati
}
\author{
    [Your Name]\
    Roll No: [Your Roll Number]\
    \vspace{1cm}
    Supervisor: Dr. Ferdous Ahmed Barbhuiya
}
\date{February 2026}

\begin{document}

% Title Page
\maketitle

% Abstract
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

This thesis investigates the application of explainable artificial intelligence (XAI) 
techniques to Docker container malware detection using vision transformers. Container 
security is a critical concern in modern cloud computing, with malware often modifying 
only a tiny fraction of the container filesystem, making detection challenging.

We extend the image-based malware detection approach by Nousias et al. (2025) by 
introducing explainability through GradCAM, SHAP, and LIME. We compare convolutional 
neural networks (CNNs) with vision transformer architectures (Swin, ViT) and evaluate 
which XAI methods best identify actual malware regions using ground-truth masks from 
the COSOCO dataset.

Furthermore, we propose a novel Hilbert curve inverse mapping technique that traces 
model attention back to specific byte offsets and files in the container filesystem, 
enabling forensic attribution. Our results show that [results to be filled] and 
demonstrate the practical utility of XAI for security analysts.

\textbf{Keywords:} Container Security, Malware Detection, Explainable AI, Vision Transformers, 
GradCAM, Docker, Deep Learning

% Table of Contents
\tableofcontents
\listoffigures
\listoftables

% Chapters
\include{chapters/01_introduction}
\include{chapters/02_literature_review}
\include{chapters/03_methodology}
\include{chapters/04_implementation}
\include{chapters/05_results}
\include{chapters/06_conclusion}

% Bibliography
\bibliographystyle{IEEEtran}
\bibliography{references}

% Appendices (optional)
% \appendix
% \chapter{Code Snippets}
% \chapter{Additional Results}

\end{document}
